Software Citation Principles

### 2016-04-05 sc-principles/software-citation-principles.tex
Section 3 suggested changes.

We have documented and analyzed a set of use cases related to software citation in \cite{SC-Use-Cases}.
Table~\ref{tab:use_cases} summarizes these use cases and makes clear what the requirements are for software citation in each case.
\scnote{Perhaps the long caption of Table 2 can be mostly moved here and be replaced with a shorter version there.}

%

@@

\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases}. ``Researcher'' includes both academic researchers (e.g., postdoc, tenure-track faculty member) and research software engineers;
``publisher'' includes both traditional publishers that publish text and\slash or software papers as well as archives such as Zenodo that directly publish software;
``reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility;
examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search;
domain groups include bioCADDIE~\cite{bioCADDIE}, Computational Infrastructure for Geodynamics (CIG)~\cite{CIG}, etc.;
``repository'' refers to public software repositories such as Astronomy Source Code Library (ASCL)~\cite{ascl},
GitHub, Netlib, Comprehensive R Archive Network (CRAN), institutional repositories;
``funder'' is a group that funds software or work using software; and
``unique ID'' refers to identifiers such as a DOI, ARK, or PURL.}

@@

Stakeholder & Use\slash wants to 	&  \rot{Software name} & \rot{Author(s)} & \rot{Version number} & \rot{Release date} & \rot{Location\slash repository} & \rot{Unique identifier} & \rot{Indexed citations} & \rot{Contributor role} & \rot{Software license}  \\

>>>>

We have documented and analyzed a set of use cases related to software citation
in \cite{SC-Use-Cases}. Table~\ref{tab:use_cases} summarizes these use cases and
makes clear what the requirements are for software citation in each case. In the following list,
we clarify a few notions used in the table.
\begin{itemize}

\item ``Researcher'' includes both academic researchers (e.g., postdoc,
tenure-track faculty member) and research software engineers;

\item ``Publisher'' includes both traditional publishers that publish text
and\slash or software papers as well as archives such as Zenodo that directly
publish software;

\item ``Repository'' refers to public software repositories such as Astronomy
Source Code Library (ASCL)~\cite{ascl}, GitHub, Netlib, Comprehensive R Archive
Network (CRAN), institutional repositories;

\item ``Funder'' is a group that funds software or work using software;

\item Examples of ``Indexer'' include Scopus, Web of Science, Google Scholar,
and Microsoft Academic Search;

\item ``Domain group'' includes bioCADDIE~\cite{bioCADDIE}, Computational
Infrastructure for Geodynamics (CIG)~\cite{CIG}, etc.;

\item ``Unique identifier'' refers to identifiers such as a DOI, ARK, or PURL;

\item``reproduce'' can mean reproduction, replication, verification, validation,
repeatability, and\slash or utility.
\end{itemize}

@@

\begin{table}[tbhp]
\caption{Use cases for software citation, adapted from~\cite{SC-Use-Cases}.}
%``Researcher'' includes both academic researchers (e.g., postdoc, tenure-track
%faculty member) and research software engineers;
%``publisher'' includes both traditional publishers that publish text and\slash or software papers as well as archives such as Zenodo that directly publish software;
%``reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility;
%examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search;
%domain groups include bioCADDIE~\cite{bioCADDIE}, Computational Infrastructure for Geodynamics (CIG)~\cite{CIG}, etc.;
%``repository'' refers to public software repositories such as Astronomy Source Code Library (ASCL)~\cite{ascl},
%GitHub, Netlib, Comprehensive R Archive Network (CRAN), institutional repositories;
%``funder'' is a group that funds software or work using software; and
%``unique ID'' refers to identifiers such as a DOI, ARK, or PURL.
%}

@@

Stakeholder & wants to 	&  \rot{Software name} & \rot{Author(s)} & \rot{Version number} & \rot{Release date} & \rot{Location\slash repository} & \rot{Unique identifier} & \rot{Indexed citations} & \rot{Contributor role} & \rot{Software license}  \\
